\documentclass{article}
\usepackage{lipsum}
\usepackage[a4paper, total={6.5in, 10in}]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\begin{document}
	\title{Computer Contest Level 1 Outline}
	\date{\today}
	\author{David Lu}
	\maketitle
	
	\section{Course Summary}
	The Computer Contest Level 1 course teaches basic contest programming, including algorithms, logic, and techniques needed to succeed in programming contests. Some programming experience is required.\\
	
	\textbf{Programs Used:} Any compiler, C++/Java preferred 
	
	\textbf{Age Range:} Grades 9-12
	
	A working laptop is required for this course (any operating system).
	
	\subsection{Outline}
	\begin{itemize}
		\item{Conditionals}
		\item{Loops}
		\item{Arrays and Strings}
		\item{Sorting}
		\item{Data Structures}
		\item{Graph Theory and Recursion}
	\end{itemize}
	
	\section{Evaluations}
	
	\subsection{Assignments}
	Homework is assigned weekly, to be due the next week. Each assignment is worth 5\%, for a total of 40\%. Assignment completion is critical to applying course material. Assignment submission/feedback is online. Assignments are not taken up in class unless a request is made. 
	
	\subsection{Quizzes}
	Quizzes are held every two weeks in class. Each quiz is worth 5\%, for a total of 20\%. Quizzes are designed to evaluate conceptual knowledge of course material. Answers are taken up in the following class.
	
	\subsection{Tests}
	Tests are held monthly in class. Each test is worth 20\%, for a total of 40\%. Answers are taken up in the following class.
	
	\section{Marking Scheme}
	
	\begin{itemize}
		\item{Assignments - 40\%}
		\item{Quizzes - 20\%}
		\item{Tests - 40\%}
	\end{itemize}
	
	\section{Contact}
	
	I can be reached at \href{mailto:dlu97@outlook.com}{dlu97@outlook.com}
	
\end{document}